\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}
\usepackage{adjustbox}

\input{../Comments}
\input{../Common}

\begin{document}

\title{System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section*{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
Date October 27 & 1.0 & Adding NFR testing plan\\
Date October 27 & 1.1 & Adding FR testing plan\\
Date October 27 & 1.2 & Added section 2 and reflection\\
Date October 27 & 1.3 & Added section 3.1 - 3.4\\
Date October 27 & 1.4 & Added implementation, automated, and software verification\\
Feb.\ 15, 2026 & 1.5 & Updated plan to match implemented scope and added unit test section\\
April 6, 2026 & 1.6 & Clarified feedback metrics, ambiguity definition, and reference warning criteria\\
\bottomrule
\end{tabularx}

~\\


\newpage

\tableofcontents

\listoftables

\newpage

\pagenumbering{arabic}


\section{General Information}

\subsection{Summary}
The software system being tested is \textbf{Sanskrit Manuscript Reconstruction Platform}, a research tool designed to assist scholars in reconstructing fragmented Buddhist manuscripts through computational analysis. The system integrates machine learning, computer vision, and local data management to enable users to upload digitized manuscript fragments, search and filter fragment collections, and visually arrange fragments on an interactive canvas. An offline machine learning (ML) pipeline provides segmentation, script classification, line counting, circle/scale detection, and related metadata; edge matching is implemented in the backend.
\newline
The verification and validation process will ensure that all core functionalities, including fragment upload, search/filtering, canvas workspace interactions, ML analysis outputs, and edge matching, perform correctly, reliably, and consistently across diverse manuscript inputs and cultural/linguistic contexts. It will also verify that data integrity and safety-critical requirements identified in the Hazard Analysis are met.
\newline
Testing will be conducted incrementally across all major milestones (Proof of Concept, Revision 0, and Revision 1) using a combination of unit testing, integration testing, usability testing, and system-level validation to confirm that the software meets its specified functional and non-functional requirements as outlined in the SRS.
  
\subsection{Objectives}

The primary objective of this Verification and Validation (V\&V) Plan is to ensure that the \textbf{Sanskrit Manuscript Reconstruction Platform} meets its defined functional and non-functional requirements, operates reliably under typical research conditions, and achieves sufficient usability for its intended audience of Buddhist Studies scholars. The V\&V process aims to build confidence in the correctness, stability, and scholarly utility of the system.

\textbf{In-Scope Objectives:}
\begin{itemize}
    \item \textbf{Functional correctness:} Verify that core workflows (fragment upload, search/filtering, canvas workspace, metadata editing, and session management) produce accurate and expected outcomes.
    \item \textbf{ML analysis integration:} Validate that pipeline outputs (segmentation, script type, line count, circle/scale detection) are generated and stored correctly for use in the UI.
    \item \textbf{Edge matching:} Validate that edge matching tooling produces reasonable candidate rankings on curated fragment pairs.
    \item \textbf{Reliability:} Validate that the system performs consistently across multiple sessions and input types, with appropriate handling of errors, interruptions, and data corruption.
    \item \textbf{Data integrity and security:} Ensure that user data, manuscript fragments, and annotations are stored securely and remain consistent, as outlined in the Safety and Security Requirements.
    \item \textbf{Usability and accessibility:} Evaluate that scholars can intuitively use the system to complete core reconstruction tasks with minimal training, supported by the usability study and user manual deliverables.
    \item \textbf{Traceability:} Establish end-to-end verification between requirements, test cases, and hazard mitigations to ensure all critical safety-related functionalities are validated.
\end{itemize}

\textbf{Out-of-Scope Objectives:}
\begin{itemize}
    \item \textbf{User authentication and role-based access control:} Account management and access control are not implemented in the current prototype.
    \item \textbf{OCR transcription assistance:} OCR-based transcription is not implemented in the current prototype.
    \item \textbf{External library verification:} The correctness of third-party libraries and frameworks (e.g., OpenCV, PyTorch, TensorFlow) will be assumed based on their established reliability and community validation.
    \item \textbf{Extensive performance benchmarking:} While basic response-time and load-handling tests will be conducted, large-scale benchmarking under production conditions is beyond the project’s resource and time constraints.
    \item \textbf{Cross-platform hardware testing:} The V\&V plan focuses on desktop deployment and does not include testing on specialized hardware or legacy systems.
    \item \textbf{Formal verification:} Mathematical proofs or model checking of algorithms are not feasible within the capstone timeline and are deferred to potential future work.
\end{itemize}

The objectives and their limitations reflect the practical constraints imposed on the team (mainly time and resources) while ensuring comprehensive coverage of functionality, usability, and safety-critical elements central to the platform’s success.


\subsection{Challenge Level and Extras}

This year’s capstone projects do not include a challenge level. Evaluation will focus on system completeness, correctness, usability, and overall technical quality.

\textbf{Extras:}

Two approved extras are included as part of this project to enhance the evaluation of usability and maintainability.

\begin{itemize}
    \item \textbf{User Manual:}  
    A comprehensive user manual will be developed to assist scholars in using the platform effectively. It will describe the main workflows such as fragment upload, search/filtering, canvas arrangement, metadata editing, and running the ML pipeline, and provide troubleshooting guidance. The manual will also include annotated screenshots and short tutorials covering both basic and advanced usage scenarios.

    \item \textbf{Usability Report:}  
    A formal usability evaluation will be conducted to assess the system’s ease of use, learnability, and effectiveness for non-technical users. Feedback will be collected from scholars in Buddhist Studies, linguists, and cultural domain experts in related fields through observation and structured task completion. The resulting report will summarize key usability metrics, identify design pain points, and provide recommendations for improvement.
\end{itemize}

These extras directly support the project’s primary goals of accessibility and scholarly usability by ensuring that end users can efficiently interact with complex AI-driven tools through a clear, guided interface.

\subsection{Relevant Documentation}

This Verification and Validation Plan references all major project documents that define the system’s motivation, requirements, development strategy, safety considerations, and user-facing deliverables for the \textbf{Sanskrit Manuscript Reconstruction Platform}. These documents collectively establish the foundation for testing and traceability throughout the project lifecycle.

\begin{itemize}
    \item \textbf{Problem Statement and Goals Document} (\citet{ProblemStatement})  
  Defines the project motivation, objectives, and expected outcomes for reconstructing fragmented Buddhist manuscripts. It helps the V\&V plan by clarifying which goals must be verified through system tests and validation activities.

    \item \textbf{Development Plan} (\citet{DevelopmentPlan})  
  Outlines the workflow structure, team responsibilities, scheduling, coding standards, and continuous integration process. It helps the V\&V plan by showing who is responsible for creating, executing, and reviewing verification tasks.

    \item \textbf{Software Requirements Specification (SRS)} (\citet{SRS-Sanskrit-Ciphers})  
  Specifies all functional and non-functional requirements, including detailed system components, interfaces, and prioritized behaviors. It helps the V\&V plan by providing the requirements that are traced directly to test cases and success criteria.

    \item \textbf{Hazard Analysis Document} (\citet{HazardAnalysis})  
  Identifies potential hazards, risk factors, and corresponding safety and security requirements that inform this V\&V plan. It helps the V\&V plan by identifying the risks that require dedicated validation and safety testing.

    \item \textbf{Design Documents (MG and MIS)} (\citet{DesignDocs})  
  To be developed in later phases. These will provide architectural decomposition, module definitions, and design rationale. They help the V\&V plan by defining the structures that must be checked during design verification and unit testing.

    \item \textbf{User Manual} (\citet{UserManual})  
  Provides detailed guidance for scholars on using the platform’s core features, including uploading, searching/filtering, canvas arrangement, metadata editing, and pipeline execution. It helps the V\&V plan by supporting usability testing and confirming that workflows are understandable.

    \item \textbf{Usability Report} (\citet{UsabilityReport})  
  Summarizes results from usability testing and participant feedback to evaluate ease of use, learnability, and overall effectiveness. It helps the V\&V plan by documenting whether the evaluated interface meets the usability targets established in the plan.
\end{itemize}

Together, these documents establish a complete record of the project’s development and verification process, ensuring traceability between requirements, design, testing, and evaluation.

\section{Plan}

This section presents the overall strategy for Verification and Validation (V\&V) of the project. It outlines how we will organize people and activities, how key artifacts will be reviewed and tested, and how results will inform subsequent work. The goal is to provide a clear, practical roadmap for building confidence in the system from requirements through delivery.


\subsection{Verification and Validation Team}

This subsection defines the project roles responsible for planning, executing, and reviewing V\&V activities. Each role has clear
primary responsibilities and an assigned independent Reviewer to ensure separation of duties and objective appraisal.
Roles may rotate by phase (requirements, design, implementation) to match expertise and workload, but accountability remains
with the named owner for the current milestone. The table below summarizes the assignments. In addition to the roles listed below, Dr.~Smith and the Teacher Assisstant (TA) review all of our work across every section of the project; however, they are not included in the table because their review applies universally rather than to specific assignments.

\begin{table}[h]
\centering
\caption{V\&V Roles and Responsibilities}
\begin{adjustbox}{max width=\textwidth,center}
\begin{tabular}{p{3.2cm} p{7.2cm} p{3cm} p{2cm}}
\toprule
\textbf{Role} & \textbf{Primary Responsibilities} & \textbf{Person} & \textbf{Reviewer}\\
\midrule
V\&V Lead & Manages the development and execution of the V\&V plan, oversees test protocols, ensures compliance, and leads root cause analysis for issues found during testing  & Dylan Garner & Aswin Kuganesan\\
V\&V Manager & Defines the overall V\&V strategy, coordinates activities across the project, manages schedules and resources, and forecasts workloads & Yousef Shahin & Umar Khan \\
Test Architect & Builds Req$\leftrightarrow$Test traceability; drafts system and NFR tests & Omar El-Aref & Yousef Shahin \\
V\&V Engineer &  Develops and executes test plans and procedures, designs test cases, documents results, and troubleshoots issues.  & Umar Khan & Dylan Garner \\
Quality Assurance & Often works closely with the V\&V team to ensure the product meets quality standards throughout the development lifecycle & Aswin Kuganesan & Omar El-Aref\\
Supervisor &  External reviewer; approves SRS baselining and risk mitigations & Dr. Shayne & \\
\bottomrule
\end{tabular}
\end{adjustbox}
\end{table}

\subsection{SRS Verification}

This subsection defines how we will verify that the SRS \citep{SRS-Sanskrit-Ciphers} is correct, complete, consistent, measurable, and feasible. We use three complementary approaches: guided reviews by TAs/peers, a supervisor-facing survey and interview that validate fundamentals in non-technical terms (translated into technical requirements), and continuous conformance checks during design/implementation against SRS use cases and fit criteria. Each approach includes instruments, process, and success metrics.

\subsubsection*{TA/Peer Guided Review (Structured Feedback)}
\textbf{Instrument.} A checklist-driven review by peers and TAs to ensure we are staying in line with the fundamentals of our requirements. Issues are filed in GitHub as feedback from TAs and peers as well as feedback on Avenue which is more detailed from the TA\\

\noindent\textbf{Process.}
\begin{enumerate}
  \item After handing in the SRS document our peers go through the document and highlight areas to improve on.
  \item Once our peers have given us feedback we are to address the feedback
  \item The TA will also go through the SRS document and provide more in depth feedback to help with the document overall
  \item Once we get the feedback for the TA we create an Issue in GitHub and address the feedback given to us
\end{enumerate}
\textbf{Success metrics.}
\begin{itemize}
  \item \textbf{Measurability coverage:} $100\%$ of distinct feedback items are resolved with a measurable change or testable requirement.
  \item \textbf{Ambiguity count:} $0$ unresolved ambiguity items remain in the SRS after rework, where an ambiguity item is any requirement statement or review comment that still needs clarification before it can be turned into a measurable fit criterion or test case.
  \item \textbf{Defect turn-around time (TAT):} All feedback has been addressed within 72 hours of being given the feedback (with a grace period of 48 hours for the entire team)
  \item \textbf{Link/xref errors:} $0$ build warnings for missing references or unresolved cross-references.
\end{itemize}

\subsubsection*{Supervisor Validation via Survey plus Interview (Non-technical \textrightarrow{} Technical)}
\textbf{Instrument.} A 10-question survey focused on \emph{fundamental product expectations}, followed by a 30\,min interview. Example survey items:
\begin{enumerate}
  \item ``The SRS describes how users start a reconstruction session and load projects.'' (1--5)
  \item ``The SRS explains the workflow for searching, filtering, and placing fragments on the canvas.'' (1--5)
  \item ``The SRS describes metadata editing and the ML pipeline used to enrich fragment data.'' (1--5)
  \item ``The SRS explains how edge-based candidate matches are produced and used.'' (1--5)
  \item Open: ``What essential research task is missing or under-specified?''
\end{enumerate}
\textbf{Process.}
\begin{enumerate}
  \item Send SRS and survey 48 hours in advance; collect responses.
  \item Hold interview; capture clarifications and priorities (top~3 must-haves).
  \item \emph{Translation step:} Requirements Analyst converts each non-technical concern into one or more technical requirements (G/S with Fit Criteria), files issues, updates traceability.
\end{enumerate}
\textbf{Success metrics.}
\begin{itemize}
  \item \textbf{Coverage score:} average score $\geq 4.0$ on survey.
  \item \textbf{Gap closure:} 100\% of supervisor ``missing/under-specified'' items mapped to new/updated requirements within 1~week.
  \item \textbf{Traceability updates:} new items appear in Req$\rightarrow$Test matrix with an assigned test type and owner.
\end{itemize}

\subsubsection*{Ongoing Conformance During Build (Design/Code \textrightarrow{} SRS)}
\textbf{Instrument.} A checklist that is shared with the team and has each module mapped to a requirement. \\
\textbf{Process.}
\begin{enumerate}
  \item For each S.4 scenario in the SRS, create at least one system test; link the implementing issue/Pull Request (PR).
  \item On each PR, the author selects related requirement from the SRS document.
  \item Monthly conformance audit: Each month the team will highlight what percentage of the requirements is done or being completed.
  \item The team will also highlight each month if they encountered a requirement that the SRS missed and make sure it is added within 48 hours of finding the missing requirement.
  \item If code conflicts with SRS, open change request: either update SRS (with rationale) or refactor code.
\end{enumerate}
\textbf{Success metrics.}
\begin{itemize}
  \item \textbf{Traceability coverage:} $\geq 95\%$ of modules or requirments can be linked to code module.
  \item \textbf{Use-case alignment:} 100\% of G.5 use cases have a corresponding S.4 detailed scenario and at least one test case.
\end{itemize}


\subsection{Design Verification}

This subsection defines how we will verify that the design documents (\textbf{Module Guide (MG)} and the \textbf{Module Interface Specification (MIS)}) is
\textbf{sound, implementable, and consistent} with the SRS \citep{DesignDocs,SRS-Sanskrit-Ciphers}. We use three complementary techniques with objective
success criteria.

\subsection*{DV-1: Unified Modeling Language (UML) Design \texorpdfstring{$\leftrightarrow$}{↔} Code Modules}

\textbf{Approach.} Maintain a living UML class diagram for core modules (front-end, backend services, Machine Learning (ML) components).
Verify code conformance on each milestone via static review (e.g., presence of classes/interfaces,
key method signatures, dependency directions).
\begin{itemize}
  \item \textbf{Procedure:}
  \begin{enumerate}
    \item Identify \emph{must-exist} types and interfaces in the UML for the current milestone.
    \item Map each UML element to its code module (file/path, namespace, class/interface name).
    \item Keep a checklist of the modules that have been mapped and the ones that still need too get created.
    \item As the design starts getting implemented we can start adjusting the UML diagram as needed.
  \end{enumerate}
  \item \textbf{Success metrics:}
  \begin{itemize}
    \item \emph{Coverage:} $\geq 95\%$ of \emph{must-exist} UML elements mapped to code modules.
    \item \emph{Directional integrity:} $0$ violations of designated dependency rules.
  \end{itemize}
\end{itemize}


\subsection*{DV-2: ML Design Soundness (Regularization/Robustness)}
\textbf{Approach.} Verify that AI/ML components are designed to generalize: regularization and robustness are evaluated with
stress tests.
\begin{itemize}
  \item \textbf{Controls implemented:} dropout (or equivalent), data augmentation, early stopping, and (where applicable) ensembles.
  \item \textbf{Ablation plan:} compare baseline vs.\ dropout, augmentation, ensemble; report mean$\pm$sd over $k$-fold Cross Validation.
  \item \textbf{Robustness:} evaluate on mildly perturbed inputs (rotation, illumination, small occlusion); report metric deltas.
  \item \textbf{Success metrics:}
    \begin{itemize}
      \item Will mainly be measured by if we found a better more robust model. Regardless of the outcome it will be a success since we have tested the models ability to generalize.
    \end{itemize}
  \item \textbf{Design outcome:} if criteria fail, document change in an ADR (e.g., add augmentation X, adjust dropout $p$, switch loss) and retest.
\end{itemize}

\subsection{Verification and Validation Plan Verification}

The V\&V plan is itself an artifact that must be verified and improved over time. We will use
peer/TA reviews, a structured test-plan walkthrough \& retrospective focused on functional and nonfunctional tests. In addition to external feedback, team members also review each other’s sections internally based on the responsibilities defined in Table 1.

\subsection*{PV-1: Classmate and TA Reviews}
\textbf{What:} External review by classmates and a course TA to assess clarity, completeness, and feasibility. \\
\textbf{How:}
\begin{itemize}
  \item Have a completed version of the V\&V plan submitted.
  \item Class peers review the plan and give feedback in an Issue on the GitHub.
  \item TA reviews the plan and confirms scope, grading-aligned expectations, and missing evidence.
  \item Each team member will create an Issue on the GitHub and fix the comments they were given on their respective parts.
\end{itemize}
\textbf{Success:} $\geq 95\%$ of actions from peer/TA reviews closed within 7 days.

\subsection*{PV-2: Test-Plan Walkthrough \& Retrospective (Functional \& Nonfunctional)}
\textbf{What:} A structured meeting to walk through current system tests (functional) and NFR tests (accessibility, privacy, performance, usability), emphasizing what has worked, what has not, and how to adapt. \\
\textbf{Inputs:} Current test catalog, pass/fail history, known pain points, and a walkthrough checklist covering: specificity of steps/data, pass/fail criteria, traceability to SRS Req IDs, reusability, and stakeholder relevance. \\
\textbf{How:}
\begin{enumerate}
  \item Lead presents the V\&V Plan document and walks through the sections asking if the team has any doubts with the current section.
  \item If a team member does have doubts about a section they would then specify. (If not the Lead moves on to the next section).
  \item The team comes up with a solution to address the doubt and clear up any misunderstadning.
  \item Team records adjustments in an Issue on the GitHub with owner and due date.
\end{enumerate}
\textbf{Success:}
\begin{itemize}
  \item Executability: 100\% of sampled tests can be executed by a third party without clarification after fixes.
  \item Specificity: Each test specifies input data, exact steps, expected outputs, and pass thresholds.
  \item Adaptation throughput: $\geq 95\%$ of improvement actions closed by next walkthrough.
\end{itemize}

\subsection{Implementation Verification}

Implementation verification will ensure that all parts of the system follow the functional requirements described in the SRS. Verification testing will include a variety of integration tests and static verification tests.  

Each module will have tests associated with it to verify correctness of input/output behavior, error handling, and data integrity. These tests will be defined in the testing plan and maintained in the continuous integration pipeline.  
\newline
\newline
\textbf{Static Verification:}
\begin{itemize}
  \item \textbf{Code walkthroughs and inspections:} Conducted by peers to ensure code quality, maintainability, and adherence to design principles.
  \item \textbf{Static analysis:} Automated tools will identify potential memory leaks, unused variables, and security vulnerabilities prior to runtime testing.
  \item \textbf{Code review sessions:} Implemented using GitHub pull requests to ensure that every commit has at least one peer review before being merged to the main branch.
\end{itemize}

\subsection{Automated Testing and Verification Tools}

Automated verification will be supported through system testing and quality assurance tools integrated into the project's continuous integration pipeline.  
\newline
\newline
\textbf{Tools and Test Frameworks:}
\begin{itemize}
  \item \textbf{System Testing:} For back-end, testing frameworks such as pytest will be used, and Jest will be used for front-end components.
  \item \textbf{Continuous Integration:} GitHub Actions for automated build, test, and deployment verification.
  \item \textbf{Static Analysis:} Coding standards will be enforced using static code analysis tools such as pylint, and static type checkers such as mypy will be used for type checking.
  \item \textbf{Test Coverage:} To measure the percentage of lines covered by automated tests, coverage.py can be used for the back-end and Jest will be used for the front-end.
  \item \textbf{Dependency and Security Scanning:} For the back-end, security scanners such as bandit will be used and npm audit will be used for frontend libraries to identify known vulnerabilities.
\end{itemize}

Test coverage metrics will be summarized in the continuous integration dashboard and reviewed regularly to ensure that important components such as data management and authentication satify quality metrics. Linting and static checks will be automatically run when the pull request is created.


\subsection{Software Validation}

Validation ensures that the implemented system meets the supervisor's requirements and satisfies its intended purpose in the academic research context. Validation will focus on confirming that reconstructed manuscripts and system functionality align with requirements.
\newline
\newline
\textbf{Validation Activities:}
\begin{itemize}
  \item \textbf{Supervisor Review Sessions:} Periodic demonstrations to the project supervisor and relevant stakeholders in the field to confirm that features meet research and usability expectations.
  \item \textbf{Cultural and Linguistic Expert Review:} Sample manuscript images and model outputs will be reviewed by our Buddhist Studies supervisor and, where available, experts in relevant linguistic and cultural domains to confirm that symbols, contexts, and annotations are interpreted appropriately.
  \item \textbf{Usability Testing:} Stakeholders will try reconstructing manuscripts to observe system functionality and performance.
  \item \textbf{Requirements Comparison Review:} Comparing system behavior with the functional and non-functional requirements in the SRS to confirm all requirements are satisfied.
  \item \textbf{Manuscript Validation:} Comparison of fragment matches generated by the system with manuscript pairings that are proven to be accurate from the same dataset.
\end{itemize}

The Rev 0 demonstration will be used to validate the requirements through feedback provided from supervisors and peers to identify software usability issues and determine final improvements prior to the project's completion.

\section{System Tests}

This section describes the system-level tests for both functional and nonfunctional requirements. Functional requirement tests verify that the system implements the specified features correctly. Nonfunctional requirement tests validate quality attributes including performance, usability, reliability, security, scalability, and compatibility. Each test case specifies the test type, initial state, input conditions, expected output, and detailed procedures for execution.

\subsection{Tests for Functional Requirements}

This section details the functional tests derived from the system’s high-priority functional requirements defined in sections S.2 and S.4 of the Requirements Standard Plan. Each test validates that the platform performs its intended scholarly and technical functions.

\subsubsection{Area of Testing 1 — Start Session and Project Loading}

These tests verify that the system fulfills requirements S.4.1 of the SRS, ensuring users can start a reconstruction session and load existing projects.

\begin{enumerate}
    \item
    \textbf{Test ID:} test-fr-session-1\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Application installed; no project loaded.\\
    \textbf{Input:} Click ``New Project'' from the home screen.\\
    \textbf{Expected Output:} Canvas workspace opens with a new project created.\\
    \textbf{Test Case Derivation:} Confirms core entry path to reconstruction workflow.\\
    \textbf{How test will be performed:} Manual UI walkthrough.\\
    \textbf{Success criteria:} Canvas loads within 3 s and project appears in recent list.\\
    \textbf{Requirement addressed:} The system shall allow users to start a reconstruction session.\\

    \item
    \textbf{Test ID:} test-fr-session-2\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Existing project saved.\\
    \textbf{Input:} Select project from home screen.\\
    \textbf{Expected Output:} Canvas opens with saved fragments restored.\\
    \textbf{How test will be performed:} Manual UI walkthrough using a known saved project.\\
    \textbf{Success criteria:} Fragment positions and transforms match saved state.\\
    \textbf{Requirement addressed:} The system shall load previous sessions.\\
\end{enumerate}

\subsubsection{Area of Testing 2 — Browse, Filter, and Place Fragments}

These tests address requirements S.4.2 of the SRS for browsing, filtering, and placing fragments on the canvas.

\begin{enumerate}
    \item
    \textbf{Test ID:} test-fr-filter-1\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Database populated with metadata.\\
    \textbf{Input:} Apply filters (e.g., line count range and script type).\\
    \textbf{Expected Output:} Sidebar list updates to matching fragments.\\
    \textbf{How test will be performed:} Manual UI test on sample dataset.\\
    \textbf{Success criteria:} Results update within 3 s and match expected counts.\\
    \textbf{Requirement addressed:} The system shall support multi-criteria filtering.\\

    \item
    \textbf{Test ID:} test-fr-canvas-1\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Sidebar populated with fragments.\\
    \textbf{Input:} Drag fragments to canvas; move, resize, rotate, lock.\\
    \textbf{Expected Output:} Fragments display and respond to transforms.\\
    \textbf{How test will be performed:} Manual UI verification with timing observations.\\
    \textbf{Success criteria:} Canvas interactions remain responsive and changes persist in memory.\\
    \textbf{Requirement addressed:} The system shall provide an interactive canvas workspace.\\
\end{enumerate}

\subsubsection{Area of Testing 3 — Save/Restore and Edge Matching}

These tests cover requirements S.4.3 for project persistence and backend edge matching.

\begin{enumerate}
    \item
    \textbf{Test ID:} test-fr-save-1\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Canvas contains arranged fragments.\\
    \textbf{Input:} Trigger save (manual or auto-save), then reload project.\\
    \textbf{Expected Output:} Canvas state is restored accurately.\\
    \textbf{How test will be performed:} Manual UI walkthrough using a saved project.\\
    \textbf{Success criteria:} Positions, rotations, sizes, and locks match saved state.\\
    \textbf{Requirement addressed:} The system shall save and restore reconstruction projects.\\

    \item
    \textbf{Test ID:} test-fr-edge-match-1\\
    \textbf{Control:} Automatic\\
    \textbf{Initial State:} Edge descriptors available for a known fragment set.\\
    \textbf{Input:} Request edge matching for a target fragment.\\
    \textbf{Expected Output:} Candidate list of matches ranked by score.\\
    \textbf{How test will be performed:} Automated backend test using curated pairs.\\
    \textbf{Success criteria:} At least three candidates returned and known pair appears in top results.\\
    \textbf{Requirement addressed:} The system shall provide edge-based match candidates.\\
\end{enumerate}

\subsubsection{Area of Testing 4 — Metadata Viewing and Editing}

These tests verify requirements S.4.4 for metadata viewing and editing.

\begin{enumerate}
    \item
    \textbf{Test ID:} test-fr-metadata-1\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Fragment available in database.\\
    \textbf{Input:} Open metadata panel; edit line count and script type.\\
    \textbf{Expected Output:} Updated values saved in the database.\\
    \textbf{How test will be performed:} Manual UI edits followed by DB verification.\\
    \textbf{Success criteria:} Updated values persist after reload.\\
    \textbf{Requirement addressed:} The system shall allow metadata edits.\\

    \item
    \textbf{Test ID:} test-fr-metadata-2\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Fragment loaded on canvas with resize applied.\\
    \textbf{Input:} Use ``Set Scale from Resize'' or edit custom fields.\\
    \textbf{Expected Output:} Scale or custom metadata saved successfully.\\
    \textbf{How test will be performed:} Manual UI test with DB verification.\\
    \textbf{Success criteria:} Fields persist and are visible after refresh.\\
    \textbf{Requirement addressed:} The system shall support scale and custom metadata editing.\\
\end{enumerate}

\subsubsection{Area of Testing 5 — Upload New Fragments}

These tests correspond to requirements S.4.5 of the SRS for adding new fragment images.

\begin{enumerate}
    \item
    \textbf{Test ID:} test-fr-upload-1\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Application running; database available.\\
    \textbf{Input:} Upload valid JPG/PNG files.\\
    \textbf{Expected Output:} Files copied to data directory and appear in sidebar.\\
    \textbf{How test will be performed:} Manual UI upload with DB verification.\\
    \textbf{Success criteria:} New fragment records exist and images load.\\
    \textbf{Requirement addressed:} The system shall allow users to upload fragment images.\\

    \item
    \textbf{Test ID:} test-fr-upload-2\\
    \textbf{Control:} Manual\\
    \textbf{Initial State:} Upload dialog open.\\
    \textbf{Input:} Attempt upload of unsupported file type.\\
    \textbf{Expected Output:} Error shown; no record created.\\
    \textbf{How test will be performed:} Manual UI test.\\
    \textbf{Success criteria:} Invalid files are rejected without side effects.\\
    \textbf{Requirement addressed:} Invalid uploads must be rejected.\\
\end{enumerate}

\subsubsection{Area of Testing 6 — ML Pipeline Enrichment}

These tests correspond to requirements S.4.6 of the SRS for running the ML pipeline and updating metadata.

\begin{enumerate}
    \item
    \textbf{Test ID:} test-fr-ml-1\\
    \textbf{Control:} Automatic\\
    \textbf{Initial State:} Pipeline configured; sample fragments available.\\
    \textbf{Input:} Run pipeline on a small batch.\\
    \textbf{Expected Output:} Segmentation and metadata fields populated in DB.\\
    \textbf{How test will be performed:} CLI run with verification of updated DB fields.\\
    \textbf{Success criteria:} Required fields (segmentation, script type, line count) are updated for processed fragments.\\
    \textbf{Requirement addressed:} The system shall update metadata via the ML pipeline.\\

    \item
    \textbf{Test ID:} test-fr-ml-2\\
    \textbf{Control:} Automatic\\
    \textbf{Initial State:} Pipeline configured with one bad image.\\
    \textbf{Input:} Run pipeline on batch containing a corrupted image.\\
    \textbf{Expected Output:} Error recorded for the bad fragment; pipeline continues.\\
    \textbf{How test will be performed:} CLI run with log and DB inspection.\\
    \textbf{Success criteria:} Processing error recorded and remaining fragments processed.\\
    \textbf{Requirement addressed:} The system shall handle pipeline errors without stopping the run.\\
\end{enumerate}

\subsection{Tests for Nonfunctional Requirements}

The following subsections detail tests for system performance, ML analysis quality, usability, reliability, data integrity, security, scalability, cross-platform compatibility, and performance benchmarking. These tests align with the nonfunctional requirements specified in the SRS document and provide measurable criteria for validating system quality attributes.

\subsubsection{System Performance Testing}

System performance testing validates ML pipeline throughput and the responsiveness of local UI workflows.

\paragraph{Collection Processing Performance}

These tests verify the system can process large collections of manuscript fragments within acceptable timeframes.

\begin{enumerate}

\item \textbf{test-nfr-perf-1}

\textbf{Type:} Dynamic, Automated, Performance

\textbf{Initial State:} Sample dataset of 500 fragments prepared for ingestion.

\textbf{Input/Condition:} Execute bulk fragment processing pipeline with the sample dataset; monitor processing time and completion rate.

\textbf{Output/Result:} Processing completes for at least 90\% of fragments in the batch; segmentation and core metadata fields are populated; system logs show no critical errors; throughput is recorded as a baseline for future comparison.

\textbf{How test will be performed:} Automated script will initiate the bulk processing workflow on the 500-fragment sample. Performance monitoring tools (e.g., time command, system resource monitors) will track execution time, CPU usage, memory consumption, and I/O operations. Upon completion, validation queries will verify that all fragments are searchable with extracted metadata. Test passes if: (1) processing time $\leq$ 1.15 hours for 500 fragments (extrapolates to $\leq$ 48 hours for full 21,000-fragment collection, meeting SRS requirement), (2) success rate $\geq$ 99\%, and (3) no memory leaks or resource exhaustion detected. Processing rate will be calculated (fragments/hour) and documented for scaling projections.

\item \textbf{test-nfr-perf-2}

\textbf{Type:} Dynamic, Automated, Performance Testing

\textbf{Initial State:} System fully operational with sample dataset (500-1000 fragments) loaded.

\textbf{Input/Condition:} Execute a scripted single-user workflow (search, filtering, canvas operations) over a 20-minute period.

\textbf{Output/Result:} Search queries return results within 3 seconds; canvas operations respond within 500 ms; 95\% of operations complete successfully without errors; no crashes or performance degradation.

\textbf{How test will be performed:} A scripted workflow will execute: (1) search by fragment ID (10\% of operations), (2) metadata filter queries (40\%), (3) canvas workspace creation with 5-10 fragments (30\%), (4) session save/restore operations (20\%). Performance metrics (response times, error rates, resource utilization) will be logged continuously. Test passes if: (1) mean search response time $\leq$ 2 seconds, (2) 95th percentile search time $\leq$ 3 seconds, (3) canvas operations complete within 500 ms, (4) error rate $\leq$ 2\%, and (5) no unhandled exceptions occur.

\end{enumerate}

\subsubsection{ML Pipeline Output Completeness}

ML pipeline tests evaluate whether required metadata outputs are generated and stored consistently for use in the UI.

\paragraph{Segmentation and Metadata Coverage}

\begin{enumerate}

\item \textbf{test-nfr-ai-1}

\textbf{Type:} Dynamic, Manual/Automated, Expert Evaluation

\textbf{Initial State:} Evaluation set of fragments with expected metadata fields.

\textbf{Input/Condition:} Run the ML pipeline on the evaluation set.

\textbf{Output/Result:} At least 90\% of fragments have segmentation coordinates and core metadata fields (script type and line count) populated; failures are logged for review.

\textbf{How test will be performed:} Query the database after the run and report coverage percentages for required fields.

\end{enumerate}

\subsubsection{Usability Testing}

Usability testing evaluates whether the system interface enables scholars to effectively perform manuscript reconstruction research tasks. These tests combine task-based user testing and systematic interface evaluation.

\paragraph{Research Workflow Task Completion}

Task-based usability testing measures whether users can successfully complete core research workflows and assesses subjective ease of use.

\begin{enumerate}

\item \textbf{test-nfr-usability-1}

\textbf{Type:} Dynamic, Manual, User Testing

\textbf{Initial State:} System fully operational with sample dataset loaded; test participants (3-4 users: project supervisor and/or 2-3 classmates) recruited; standardized task scenarios prepared

\textbf{Input/Condition:} Each participant performs 5-6 representative research tasks: (1) search for specific fragment by ID, (2) apply metadata filters, (3) create canvas workspace, (4) arrange 3-5 fragments on canvas, (5) save session, (6) restore previous session

\textbf{Output/Result:} Task completion rate $\geq$ 80\% across all participants and tasks (per SRS NFR criteria); average task completion time within specified targets; no more than 1 critical usability issue preventing task completion; participants rate overall ease of use as "easy" or "very easy" for $\geq$ 70\% of tasks

\textbf{How test will be performed:} Participants will complete tasks in a moderated usability testing session (30-45 minutes per participant). For each task, observers will record: completion status (success/fail/partial), time-on-task, number of errors, assistance required, and participant comments. Task-level success criteria: Task 1-2 (search/filter): $\leq$ 2 minutes each; Task 3-4 (canvas): $\leq$ 3 minutes each; Task 5-6 (save/restore): $\leq$ 1 minute each.

Post-test questionnaire (5-point Likert scale for each task):
\begin{itemize}
\item Q1-Q6: "How easy was it to complete Task [1-6]?" (1=Very Difficult, 2=Difficult, 3=Neutral, 4=Easy, 5=Very Easy)
\item Q7: "What was the most confusing aspect of the system?" (open-ended)
\item Q8: "What feature did you find most helpful?" (open-ended)
\item Q9: "Would you recommend this system to colleagues for manuscript research?" (Yes/No/Maybe)
\end{itemize}

Test passes if: (1) overall task completion rate $\geq$ 80\% (aligns with SRS NFR requirement), (2) $\geq$ 70\% of individual task ratings (Q1-Q6) are 4 or 5 ("easy" or "very easy"), and (3) no more than 1 critical usability issue identified that completely blocks task completion.

\item \textbf{test-nfr-usability-2}

\textbf{Type:} Static, Manual, Interface Evaluation

\textbf{Initial State:} System interface fully implemented and accessible for evaluation; usability evaluation criteria checklist prepared

\textbf{Input/Condition:} 2 team members (who did not design the specific interface components being evaluated) independently evaluate the interface against core usability principles

\textbf{Output/Result:} Consolidated report identifying usability issues categorized by principle and severity (critical, major, minor); no more than 3 critical violations identified; prioritized list of recommended improvements documented

\textbf{How test will be performed:} Each team member evaluator will spend 1-2 hours systematically exploring the interface and documenting usability issues. Evaluators will use a standardized checklist covering core usability principles:

\textbf{Evaluation Checklist:}
\begin{enumerate}
\item \textbf{Clarity}: For each major interface element (search bar, filter panel, canvas controls), is it clear what actions are available and what they do? Rate: Pass/Fail with examples.
\item \textbf{Feedback}: When performing actions (search, drag fragment, save session), does the system provide clear visual or textual feedback? Rate: Pass/Fail with examples.
\item \textbf{Consistency}: Are similar operations (e.g., all "save" actions, all "delete" actions) performed in similar ways? Rate: Pass/Fail with examples.
\item \textbf{Error Prevention \& Recovery}: Can users prevent errors (confirmation dialogs) and recover from mistakes (undo, clear error messages)? Rate: Pass/Fail with examples.
\item \textbf{Efficiency}: Can users accomplish core tasks (search → filter → canvas → save) with minimal unnecessary steps? Count steps for each workflow. Rate: Pass/Fail.
\item \textbf{Learnability}: Can a new user understand how to perform basic search and canvas operations without documentation? Rate: Pass/Fail with observations.
\end{enumerate}

For each issue identified, document: (1) specific location/feature, (2) principle violated, (3) severity rating (critical/major/minor), (4) screenshot or description, (5) suggested fix. Severity definitions: critical (prevents task completion), major (causes significant frustration or confusion), minor (cosmetic or minor inconvenience). Team will meet to consolidate findings and create prioritized issue list. Test passes if: (1) no more than 3 critical violations identified, (2) evaluation report completed documenting all findings with specific examples, and (3) critical issues have documented remediation plans before final release.

\end{enumerate}

\subsubsection{System Availability and Reliability}

Reliability testing validates stability under repeated use and recovery from interruptions without data loss.

\paragraph{Stability Under Repeated Use}

\begin{enumerate}

\item \textbf{test-nfr-reliability-1}

\textbf{Type:} Dynamic, Automated, Reliability Testing

\textbf{Initial State:} Desktop app installed with sample dataset loaded.

\textbf{Input/Condition:} Daily automated smoke test for 7 days: launch app, run search/filter, open canvas, save and reload project, then exit.

\textbf{Output/Result:} $\geq$ 95\% of runs complete without errors; database remains consistent with no corruption.

\textbf{How test will be performed:} Scripted smoke test logs pass/fail for each run; failures recorded with timestamps and logs.

\item \textbf{test-nfr-reliability-2}

\textbf{Type:} Dynamic, Manual, Recovery

\textbf{Initial State:} Project open with unsaved changes.

\textbf{Input/Condition:} Force-close the application during save; restart and reload the project.

\textbf{Output/Result:} App restarts cleanly; project data is either preserved or rolled back without corruption.

\textbf{How test will be performed:} Manual recovery test with database integrity check after restart.

\end{enumerate}

\subsubsection{Data Integrity and Security}

Data integrity and security testing ensures that fragment metadata and local file paths are preserved accurately and that the system protects against common security vulnerabilities.

\paragraph{Data Preservation and Attribution}

These tests verify that all fragment data maintains referential integrity and proper attribution throughout the system lifecycle.

\begin{enumerate}

\item \textbf{test-nfr-data-1}

\textbf{Type:} Functional, Automated, Data Validation
					
\textbf{Initial State:} Sample dataset and user-uploaded images loaded into the system.
					
\textbf{Input/Condition:} Execute comprehensive data validation checks across the collection.
					
\textbf{Output/Result:} 100\% of fragments have required fields populated; image paths point to existing files; no corruption or loss of metadata fields.
					
\textbf{How test will be performed:} Automated validation script will query all fragments in the database and verify metadata integrity.

\textbf{Required Metadata Fields:}
\begin{itemize}
\item \textbf{Fragment ID}: Unique identifier (non-null, unique constraint)
\item \textbf{Image Path}: Location of fragment image (non-null, valid path)
\item \textbf{Timestamp}: Date added to system (non-null)
\end{itemize}

Validation checks: (1) all required fields present and non-null, (2) image files exist on disk, (3) referential integrity verified (no orphaned records). Script generates exception report listing any fragments with missing/inconsistent data. Test passes with 100\% of fragments having all required fields populated.

\item \textbf{test-nfr-data-2}

\textbf{Type:} Static, Manual, Code Review

\textbf{Initial State:} Data handling and IPC modules identified for review; security review checklist prepared.

\textbf{Input/Condition:} Security-focused code review conducted by team members not primarily responsible for implementing the reviewed modules, supplemented by automated security scanning tools.

\textbf{Output/Result:} Review checklist completed with findings documented; no critical security vulnerabilities identified; common security best practices verified (input validation, SQL injection prevention, safe file handling).

\textbf{How test will be performed:} Two team members (preferably those who did not write the security-critical code) will conduct peer code review focusing on security aspects. Review checklist will cover: (1) input validation and sanitization for user-provided data, (2) SQL injection prevention (parameterized queries), (3) safe file path handling in IPC, (4) secure handling of local secrets or API keys (not committed to repository). Additionally, run automated security scanning tools appropriate for the tech stack (e.g., npm audit for Node.js, Bandit for Python, pip-audit, or built-in IDE security warnings). All findings documented with severity ratings (critical/high/medium/low). Test passes if: (1) no critical or high-severity vulnerabilities identified in manual review, (2) checklist completed for all security-critical modules, (3) automated scanning shows no critical issues, and (4) any medium/low findings have documented remediation plans or accepted risk justifications.

\end{enumerate}

\subsubsection{Scalability Testing}

Scalability testing analyzes how system performance changes as the fragment collection size increases, providing data to support future scaling decisions.

\paragraph{Fragment Collection Scalability}

This test measures system performance with varying dataset sizes to project scalability to larger fragment collections.

\begin{enumerate}

\item \textbf{test-nfr-scale-1}

\textbf{Type:} Dynamic, Manual, Scalability Analysis

\textbf{Initial State:} System operational with sample dataset (500 fragments); ability to add additional test data

\textbf{Input/Condition:} Test system performance with incrementally larger datasets: 500 fragments (baseline), 2,000 fragments, 5,000 fragments

\textbf{Output/Result:} Performance metrics documented for each dataset size showing how system scales; search response times remain acceptable ($\leq$ 5 seconds) at 5,000 fragments; documented analysis of expected performance at full 21,000-fragment scale based on observed trends

\textbf{How test will be performed:} Using existing sample data (500 fragments), create duplicate test data to reach 2,000 and 5,000 fragments (duplicates acceptable for testing purposes). At each dataset size, execute standardized queries: (1) fragment ID search (10 queries, measure average time), (2) single metadata filter (10 queries, measure average time), (3) multi-criteria filter with 2-3 filters (5 queries, measure average time). Record response times and database query execution times. Document results in simple table showing dataset size vs. average response time for each query type. Analyze trend (linear, logarithmic, exponential) and extrapolate to 21,000 fragments. Test passes if response times remain usable ($\leq$ 5 seconds) at 5,000 fragments and trend analysis suggests acceptable performance at full scale.

\end{enumerate}

\subsubsection{Cross-Platform Compatibility}

Cross-platform compatibility testing ensures that the desktop application functions correctly across supported operating systems used by researchers.

\paragraph{Desktop Compatibility Testing}

This test verifies that core functionality operates consistently across Windows and macOS (Linux optional if available).

\begin{enumerate}

\item \textbf{test-nfr-compat-1}

\textbf{Type:} Manual, Dynamic, Compatibility Testing
					
\textbf{Initial State:} Application packaged or run in development mode on each target OS.
					
\textbf{Input/Condition:} Access system and perform core workflows on multiple operating systems: Windows and macOS (Linux optional if available).
					
\textbf{Output/Result:} All core functionality (search, filter, canvas, upload, project save/load) operates correctly across tested platforms; no critical OS-specific bugs identified.
					
\textbf{How test will be performed:} Test team will execute standardized test suite on each OS.

\textbf{Test Suite (perform on each platform):}
\begin{enumerate}
\item \textbf{Search Test}: Enter fragment ID "BL-12345" in search bar, verify results display correctly
\item \textbf{Filter Test}: Apply metadata filter (e.g., "Script: Brahmi"), verify filtered results
\item \textbf{Canvas Creation}: Click "New Project", verify canvas workspace opens
\item \textbf{Drag-and-Drop}: Drag 2 fragment images onto canvas, verify they appear and can be repositioned
\item \textbf{Image Rendering}: Verify fragment images load at full resolution and display correctly
\item \textbf{Session Save}: Save canvas session, verify success message
\item \textbf{Session Restore}: Reopen the saved project, verify fragments reappear in correct positions
\item \textbf{Upload Test}: Upload a new fragment image, verify it appears in the fragment list
\end{enumerate}
\textbf{Target Platforms:} Windows 10/11 (primary development OS), macOS (if team has access); Linux optional.

For each test-platform combination, record: Pass/Fail, any errors/warnings, visual issues, performance notes. Issues documented with severity (critical/major/minor) and OS-specific details. Test passes if all critical functionality works on Windows and at least one additional OS. Issues on secondary platforms documented for future work.

\end{enumerate}

\subsubsection{Performance Benchmarking}

Performance benchmarking establishes baseline metrics for system response times that can be used for regression testing in future development.

\paragraph{Response Time Measurement}

This test documents average response times for common operations to establish performance baselines.

\begin{enumerate}

\item \textbf{test-nfr-bench-1}

\textbf{Type:} Dynamic, Manual, Benchmark Testing

\textbf{Initial State:} System operational with sample dataset (500-1000 fragments)

\textbf{Input/Condition:} Execute standardized set of operations representing typical usage patterns: (1) fragment ID search, (2) single metadata filter, (3) multi-criteria filter (2-3 criteria), (4) canvas operations with 5-10 fragments

\textbf{Output/Result:} Performance report documenting average response times for each operation type; simple table showing mean response time for each operation; baseline metrics documented for future regression testing

\textbf{How test will be performed:} For each operation type, execute 10 test runs and record response times using Electron dev tools or a simple timing script. Calculate average (mean) response time for each operation type. Document results in simple table format: Operation Type | Average Response Time | Notes. Example acceptable targets: ID search $\leq$ 1 second, single filter $\leq$ 2 seconds, multi-filter $\leq$ 3 seconds, canvas operations $\leq$ 2 seconds. This benchmark establishes baseline performance metrics for future comparison rather than strict pass/fail criteria. Results provide data for identifying performance regressions in future releases.

\end{enumerate}


\newpage
\subsection{Traceability Between Test Cases and Requirements}

\begin{table}[ht]
    \centering
    \begin{tabular}{|p{2cm}|p{4cm}|p{4cm}|p{2.5cm}|}
        \hline
        \textbf{Req. ID} & \textbf{Description} & \textbf{Test ID(s)} & \textbf{Method} \\
        \hline
        S.4.1 & Start a reconstruction session & test-fr-session-1, test-fr-session-2 & Manual \\
        \hline
        S.4.2 & Browse, filter, and place fragments & test-fr-filter-1, test-fr-canvas-1 & Manual \\
        \hline
        S.4.3 & Save and restore projects; edge matching & test-fr-save-1, test-fr-edge-match-1 & Manual and automated \\
        \hline
        S.4.4 & View and edit metadata & test-fr-metadata-1, test-fr-metadata-2 & Manual \\
        \hline
        S.4.5 & Upload new fragments & test-fr-upload-1, test-fr-upload-2 & Manual \\
        \hline
        S.4.6 & Run ML pipeline for enrichment & test-fr-ml-1, test-fr-ml-2 & Automated \\
        \hline
    \end{tabular}
    \caption{Traceability for Functional Requirements}
\end{table}

% \subsubsection{Non-Functional Requirements Traceability}
\newpage
\begin{table}[ht]
    \centering
    \begin{tabular}{|p{2cm}|p{4cm}|p{4cm}|p{2.5cm}|}
        \hline
        \textbf{Req. ID} & \textbf{Description} & \textbf{Test ID(s)} & \textbf{Method} \\
        \hline
        S.6, E.3 & System performance & test-nfr-perf-1, test-nfr-perf-2 & Automated \\
        \hline
        S.6 & ML pipeline output completeness & test-nfr-ai-1 & Manual/automated eval \\
        \hline
        S.6, S.2.1 & Usability & test-nfr-usability-1, test-nfr-usability-2 & Manual testing \\
        \hline
        S.6, S.2.2 & Reliability & test-nfr-reliability-1, test-nfr-reliability-2 & Automated and manual \\
        \hline
        E.6, S.6, E.3 & Data integrity and security & test-nfr-data-1, test-nfr-data-2 & Automated and code review \\
        \hline
        E.3, S.6 & Scalability & test-nfr-scale-1 & Manual analysis \\
        \hline
        S.2.1 & Cross-platform compatibility & test-nfr-compat-1 & Manual \\
        \hline
        S.6 & Performance benchmarking & test-nfr-bench-1 & Manual benchmark \\
        \hline
    \end{tabular}
    \caption{Traceability for Non-Functional Requirements}
\end{table}

\section{Unit Test Description}

Unit testing focuses on deterministic modules identified in the MIS, particularly the ML pipeline utilities and database access layer. Tests are implemented with PyTest in \texttt{src/ml\_pipeline/tests}.

\subsection{Unit Testing Scope}

\textbf{In scope:} \texttt{ml\_pipeline.core.utils}, \texttt{ml\_pipeline.core.registry}, and \texttt{ml\_pipeline.core.database}.  
\textbf{Out of scope:} GPU-heavy model inference/training, Electron UI components, and full IPC integration (covered by integration/system tests).

\subsection{Tests for Functional Requirements}

\subsubsection{ML Pipeline Utilities (\texttt{ml\_pipeline.core.utils})}

\begin{enumerate}
\item \textbf{test-ut-utils-1}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Temporary base directory.\\
Input: Relative and absolute paths.\\
Output: Correct resolved path.\\
Test Case Derivation: Ensures path resolution works for both relative and absolute inputs.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_utils.py}.\\

\item \textbf{test-ut-utils-2}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Missing config file.\\
Input: Non-existent config path.\\
Output: \texttt{FileNotFoundError}.\\
Test Case Derivation: Verifies invalid configuration paths are rejected.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_utils.py}.\\

\item \textbf{test-ut-utils-3}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Valid YAML config in temp directory.\\
Input: Config path.\\
Output: Parsed configuration dictionary.\\
Test Case Derivation: Confirms correct YAML parsing.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_utils.py}.\\

\item \textbf{test-ut-utils-4}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Temporary log directory.\\
Input: Logging configuration with file path.\\
Output: Log files created (pipeline log and error log).\\
Test Case Derivation: Verifies logging setup writes to expected files.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_utils.py}.\\
\end{enumerate}

\subsubsection{Processor Registry (\texttt{ml\_pipeline.core.registry})}

\begin{enumerate}
\item \textbf{test-ut-registry-1}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Empty registry.\\
Input: Register and retrieve a dummy processor.\\
Output: Retrieved class matches the registered class.\\
Test Case Derivation: Confirms registry bookkeeping and lookup.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_registry.py}.\\

\item \textbf{test-ut-registry-2}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Empty registry.\\
Input: Request an unknown processor name.\\
Output: \texttt{KeyError}.\\
Test Case Derivation: Ensures missing processors are reported.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_registry.py}.\\
\end{enumerate}

\subsubsection{Database Manager (\texttt{ml\_pipeline.core.database})}

\begin{enumerate}
\item \textbf{test-ut-db-1}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Temporary SQLite database with sample fragments.\\
Input: Query all fragments.\\
Output: List of \texttt{FragmentRecord} objects with expected IDs.\\
Test Case Derivation: Validates mapping from DB rows to records.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_database.py}.\\

\item \textbf{test-ut-db-2}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Temporary SQLite database with one fragment.\\
Input: Update fragment fields.\\
Output: Updated values persisted in DB.\\
Test Case Derivation: Confirms update queries commit correctly.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_database.py}.\\

\item \textbf{test-ut-db-3}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Temporary SQLite database with mixed processing statuses.\\
Input: Request processing statistics.\\
Output: Correct totals for completed/pending/failed.\\
Test Case Derivation: Ensures aggregate queries return correct counts.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_database.py}.\\

\item \textbf{test-ut-db-4}\\
Type: Functional, Dynamic, Automatic\\
Initial State: Temporary SQLite database with completed fragments and timestamps.\\
Input: Request last processed ID.\\
Output: Correct fragment ID returned.\\
Test Case Derivation: Ensures ordering by timestamp works as expected.\\
How test will be performed: PyTest in \texttt{src/ml\_pipeline/tests/test\_database.py}.\\
\end{enumerate}

\subsection{Tests for Nonfunctional Requirements}

Unit tests are not the primary mechanism for NFR verification. NFRs are evaluated at the system and integration levels (see Section 4).

\subsection{Traceability Between Test Cases and Modules}

\begin{table}[ht]
    \centering
    \begin{tabular}{|p{5cm}|p{7cm}|}
        \hline
        \textbf{Module} & \textbf{Unit Test ID(s)} \\
        \hline
        \texttt{ml\_pipeline.core.utils} & test-ut-utils-1 to test-ut-utils-4 \\
        \hline
        \texttt{ml\_pipeline.core.registry} & test-ut-registry-1 to test-ut-registry-2 \\
        \hline
        \texttt{ml\_pipeline.core.database} & test-ut-db-1 to test-ut-db-4 \\
        \hline
    \end{tabular}
    \caption{Traceability Between Unit Tests and Modules}
\end{table}
				
\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\newpage

\section{Appendix}

This is where you can place additional information.

\subsection{Symbolic Parameters}

The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
Their values are defined in this section for easy maintenance.

\subsection{Usability Survey Questions?}

\wss{This is a section that would be appropriate for some projects.}

\newpage{}
\section*{Appendix --- Reflection}

\wss{This section is not required for CAS 741}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable? 
  
  \hspace{2em} The fact that we had a solid base from our SRS to work from was one of this deliverable's strongest points. We were able to directly map the SRS's structured sections and clearly defined functional requirements into test areas, which greatly streamlined the planning process. Assigning ownership for test design and documentation was also simple because we had already finished the Development Plan and each of us knew our general responsibilities. This helped us stay organized. Throughout this phase, we worked effectively as a team, checked each other's sections for coherence, and developed trust that the verification plan related to our earlier work.

  \item What pain points did you experience during this deliverable, and how
    did you resolve them?

  \hspace{2em} Time management was our biggest challenge during this phase, as the deliverable overlapped with midterms and major assignments in other courses. We initially underestimated how much time would be required to properly structure the test cases and trace them back to the requirements. Since our platform integrates multiple components (front end, back end, and multiple AI/ML services), defining the boundaries between modules for testing was another significant challenge. This took longer than anticipated. In order to resolve this, we had brief group discussions to determine which system components would be verified at the unit level as opposed to the system level. These discussions also made sure that everyone understood the differences between validation and verification in the context of our platform. By the end, we were more assured of how we divided up the work and how we interpreted the testing scope.

  \item What knowledge and skills will the team collectively need to acquire to
  successfully complete the verification and validation of your project?
  Examples of possible knowledge and skills include dynamic testing knowledge,
  static testing knowledge, specific tool usage, Valgrind etc.  You should look to
  identify at least one item for each team member.\hspace{2em} To carry out the next stages of verification effectively, our team identified several areas for skill development. We need to strengthen our understanding of automated testing frameworks, particularly PyTest and coverage.py, to ensure consistent and maintainable test execution. We also plan to expand our familiarity with static and dynamic analysis tools like Ruff, MyPy, and Bandit for enforcing code quality and identifying potential vulnerabilities. Another important learning area will be validating the accuracy and robustness of our machine learning models — for example, evaluating OCR performance using accuracy metrics, confusion matrices, and ground truth comparison datasets. Collectively, these skills will help us achieve more objective, measurable verification results and reduce the likelihood of regression errors in later phases.

  \hspace{2em} To carry out the next stages of verification effectively, our team identified several areas for skill development. We need to strengthen our understanding of automated testing frameworks, particularly PyTest and coverage.py, to ensure consistent and maintainable test execution. We also plan to expand our familiarity with static and dynamic analysis tools like Ruff, MyPy, and Bandit for enforcing code quality and identifying potential vulnerabilities. Another important learning area will be validating the accuracy and robustness of our machine learning models, for example, evaluating OCR performance using accuracy metrics, confusion matrices, and ground truth comparison datasets. Collectively, these skills will help us achieve more objective, measurable verification results and reduce the likelihood of errors in later phases.

  \item For each of the knowledge areas and skills identified in the previous
  question, what are at least two approaches to acquiring the knowledge or
  mastering the skill?  Of the identified approaches, which will each team
  member pursue, and why did they make this choice?

  \hspace{2em} As a team, we plan to take a mixed approach that combines self-learning, collaborative practice, and direct application within the project. To establish a technical foundation, everyone in the group will adhere to the PyTest, coverage.py, and static analysis tools' official documentation and focused tutorials. Then, using GitHub Actions to run automated tests continuously and track coverage over time, we will further solidify this learning by implementing them early in the development process. We intend to incorporate brief knowledge-sharing periods into our weekly team meetings, where a team member can show the others a testing or verification method. In order to guide our validation setup for the AI components, we plan to review open-source evaluation scripts from Optical Character Recognition(OCR) and similarity-based matching research papers.  This collaborative, iterative approach ensures that every member not only understands the testing tools but also applies them meaningfully within their assigned subsystem.

\end{enumerate}

\end{document}
