\documentclass[12pt, titlepage]{article}

\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{float}
\usepackage{placeins}
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Verification and Validation Report: \progname} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Notes}\\
\midrule
March 3, 2026 & 1.0 & Initial complete V\&V report populated from project artifacts and verification scripts.\\
\bottomrule
\end{tabularx}

~\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  FR & Functional Requirement\\
  NFR & Nonfunctional Requirement\\
  CI & Continuous Integration\\
  OCR & Optical Character Recognition\\
  ML & Machine Learning\\
  UI & User Interface\\
  V\&V & Verification and Validation\\
  \bottomrule
\end{tabular}\\

\newpage

\tableofcontents

\listoftables %if appropriate

\listoffigures %if appropriate

\newpage

\pagenumbering{arabic}

This document reports the verification and validation outcomes for the Sanskrit Ciphers project based on implemented code, available scripts, and documentation artifacts in the repository as of March 3, 2026. The report records what has been validated, what remains partially validated, and how evidence traces to requirements and modules.

\section{Functional Requirements Evaluation}

Functional evaluation was performed using integration scripts, processor registration checks, configuration inspection, and implementation checklists.

\begin{table}[htbp]
\centering
\caption{Functional Requirement Evaluation Summary}
\begin{tabularx}{\textwidth}{p{1.5cm}p{4.2cm}p{5.5cm}p{2cm}}
\toprule
\textbf{Req.} & \textbf{Capability} & \textbf{Evidence} & \textbf{Status}\\
\midrule
S.4.1 & Authentication and secure access & Planned in VnV plan; no dedicated automated authentication test artifact found in this repository snapshot. & Partial\\
S.4.2 & Upload and preprocessing pipeline & Processor architecture and orchestrator flow are implemented and configured in the ML pipeline. & Pass\\
S.4.3 & Fragment matching and reconstruction workflow & Matching-related modules are present and reflected in planned VnV test definitions. & Partial\\
S.4.4 & Script type classification & Integration implementation and checks are documented in project implementation summaries, checklists, and verification scripts. & Pass\\
S.4.5 & OCR and transcription assistance & OCR-related pipeline components and configuration entries exist; a consolidated end-to-end accuracy report is not included in this snapshot. & Partial\\
S.4.6 & Search, filter, and export workflows & Requirement-test mapping and test definitions appear in VnV plan (database search and CSV export cases). & Partial\\
\bottomrule
\end{tabularx}
\end{table}

\paragraph{Observed execution evidence.}
Running the quick verification script attempted full registry discovery and reached heavy ML dependency imports before interruption. This indicates the discovery path executes into processor imports, but full end-to-end runtime confirmation for all processors depends on complete environment and dependency availability.

\section{Nonfunctional Requirements Evaluation}

\subsection{Usability}

The project includes a User Guide deliverable path and usability test planning in the VnV plan. In this repository snapshot, the primary evidence is planning and documentation structure rather than completed quantitative usability study results.

\textbf{Status:} Partial validation (process and instruments defined; final measured outcomes not centrally recorded in this report source set).
		
\subsection{Performance}

Performance criteria and procedures are defined in the VnV plan (for example, throughput and concurrent-user scenarios). The repository currently contains processor configurations and model artifacts, but does not include a consolidated benchmark result log in the report directory.

\textbf{Status:} Partial validation (test design complete; final benchmark dataset/results file not found in this snapshot).

\subsection{etc.}

\textbf{Reliability and Recoverability:} Recovery and uptime tests are defined in the VnV plan. No consolidated runtime uptime report artifact is present in this repository snapshot.\\
\textbf{Data Integrity:} Schema and migration paths are tested indirectly by integration scripts, with checklist confirmation of script-type fields.\\
\textbf{Security:} Security scanning tools are listed in plan; no generated scan report artifact is stored in this snapshot.
	
\section{Comparison to Existing Implementation}	

This project reused an existing ML pipeline architecture and extended it with a script-type classifier. The new processor follows the same design contract as existing processors:

\begin{itemize}
  \item Same processor abstraction and lifecycle methods.
  \item Same auto-discovery mechanism through the processor registry.
  \item Same orchestrated execution and update flow through the pipeline orchestrator.
  \item Same configuration-driven enable and disable pattern.
\end{itemize}

Compared to the pre-integration state, the repository now includes dedicated integration documentation and verification scripts for script-type classification, improving traceability and maintainability of this feature.

\section{Unit Testing}

Current verification in this repository is primarily script-based integration verification rather than a formal unit-test suite.

\begin{table}[htbp]
\centering
\caption{Implemented Script-Based Test Checks}
\begin{tabularx}{\textwidth}{p{3.2cm}p{6.5cm}p{2.6cm}p{1.8cm}}
\toprule
\textbf{Artifact} & \textbf{Purpose} & \textbf{Type} & \textbf{Status}\\
\midrule
Quick verification script & Processor import, registry discovery, dataclass field checks, and config-model presence checks. & Integration smoke & Partial runtime (interrupted during dependency import)\\
Comprehensive verification script & End-to-end integration checks for script-type classification. & Integration validation & Available\\
Pipeline integration verifier & Confirms processor registration and pipeline-level configuration integration. & Integration smoke & Available\\
Script-type processor test script & Exercises model loading and sample fragment classification path. & Component/integration & Available\\
\bottomrule
\end{tabularx}
\end{table}

\textbf{Assessment:} Unit-level confidence for core scripts is moderate; strongest evidence is integration-oriented. A dedicated automated unit-test suite remains a recommended improvement.

\section{Changes Due to Testing}

Testing and integration verification drove concrete implementation changes:

\begin{itemize}
  \item Added processor support fields to fragment records for script-type confidence tracking.
  \item Added processor exports and registration compatibility.
  \item Added and updated pipeline configuration for script-type classification and thresholds.
  \item Added verification and usage artifacts, including implementation checklists and integration scripts.
\end{itemize}

These changes improved observability (clear verification scripts), reproducibility (documented commands), and schema support for the new ML output fields.

\section{Automated Testing}

Automated checks in this repository are currently command/script driven:

\begin{itemize}
  \item Python verification scripts for quick and comprehensive integration checks.
  \item Orchestrator-driven pipeline execution through the CLI.
  \item Checklist-based validation artifacts.
\end{itemize}

The automation strategy is functional for integration checks but should be strengthened with standardized CI test jobs and formal unit test collection.
		
\section{Trace to Requirements}

\begin{table}[htbp]
\centering
\caption{Requirement to Verification Trace Matrix}
\begin{tabularx}{\textwidth}{p{1.5cm}p{3.8cm}p{6.2cm}p{2cm}}
\toprule
\textbf{Req.} & \textbf{Requirement Summary} & \textbf{Evidence/Test Artifacts} & \textbf{Coverage}\\
\midrule
S.4.1 & Authentication/login workflow & VnV plan tests: test-fr-auth-1, test-fr-auth-2 (plus remaining authentication cases in same group). & Planned/Partial\\
S.4.2 & Upload and preprocessing & VnV plan tests: test-fr-upload-1, test-fr-upload-2, plus preprocess group; implementation path in orchestrator and processor config. & Partial to Pass\\
S.4.3 & Matching and reconstruction & VnV plan tests: test-fr-fragment-matching-1 and test-fr-fragment-matching-2; module support in edge matching and edge-detection processor. & Partial\\
S.4.4 & Script identification & Verification scripts \path{quick_verify.py}, \path{verify_all.py}, and \path{src/ml_pipeline/verify_integration.py}; implementation checklist and completion docs. & Pass\\
S.4.5 & OCR/transcription & VnV plan script-identification and transcription test area plus OCR-capable module \path{src/ml_pipeline/processors/scale_detection_easyocr.py}. & Partial\\
S.4.6 & Search/filter/export & VnV plan tests: test-fr-database-search-1 and test-fr-database-search-2 (including CSV export validation). & Planned/Partial\\
NFR-Perf & Throughput/response under load & VnV plan tests: test-nfr-perf-1 and test-nfr-perf-2 with defined thresholds and workload profiles. & Planned\\
NFR-Usability & Task completion and UX quality & VnV plan tests: test-nfr-usability-1 and test-nfr-usability-2; supporting user-guide artifacts under \path{docs/UserGuide}. & Planned/Partial\\
NFR-Reliability & Availability and recovery & VnV plan tests: test-nfr-reliability-1 and test-nfr-reliability-2 (uptime and recovery scenarios). & Planned\\
NFR-Data/Sec & Integrity, attribution, security checks & VnV plan test-nfr-data-1 and related data/security checks; script evidence from migration and schema verification in \path{verify_all.py}. & Partial\\
\bottomrule
\end{tabularx}
\end{table}
\FloatBarrier
		
\section{Trace to Modules}		

\begin{table}[htbp]
\centering
\caption{Module to Verification Artifact Trace}
\begin{tabularx}{\textwidth}{p{4.8cm}p{6.5cm}p{2.8cm}}
\toprule
\textbf{Module} & \textbf{Verification Evidence} & \textbf{Status}\\
\midrule
\path{src/ml_pipeline/core/registry.py} & Discovery exercised by \path{quick_verify.py} and \path{src/ml_pipeline/verify_integration.py}. & Partial runtime / Pass artifact\\
\path{src/ml_pipeline/core/orchestrator.py} & Execution flow and processor initialization traced through CLI and config inspection. & Partial\\
\path{src/ml_pipeline/core/processor.py} & FragmentRecord field checks (including script-type fields) in \path{quick_verify.py} and \path{verify_all.py}. & Pass\\
\path{src/ml_pipeline/core/database.py} & Migration and schema-related checks referenced in \path{verify_all.py}. & Pass artifact\\
\path{src/ml_pipeline/processors/script_type_classification_processor.py} & Import, registry visibility, metadata validation, and checklist trace in integration docs/scripts. & Pass\\
\path{src/ml_pipeline/config.yaml} & Processor enablement, model paths, and threshold settings validated by verification scripts. & Pass\\
\path{src/classification/output/meta.json} and \path{src/models/script_type/best_model.pt} & Model and metadata artifact existence confirmed; evaluation scripts \path{src/classification/quick_eval.py} and \path{src/classification/eval_test.py} available. & Partial\\
\bottomrule
\end{tabularx}
\end{table}
\FloatBarrier

\section{Code Coverage Metrics}

No centralized line-coverage report (for example, from a Python coverage tool or Jest) was found in this repository snapshot.

\textbf{Current measurable coverage proxy:}
\begin{itemize}
  \item Presence of targeted integration verification scripts for pipeline registration, configuration, and schema interactions.
  \item Feature-level checklists indicating implemented verification points for script-type classification.
\end{itemize}

\textbf{Recommended next step:}
Add automated coverage collection for backend Python modules and publish coverage artifacts as part of CI to complement current integration-level evidence.

\FloatBarrier
\bibliographystyle{plainnat}
\bibliography{../../refs/References}

\FloatBarrier
\clearpage
\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Reflection.

\input{../Reflection.tex}

\begin{enumerate}
  \item What went well while writing this deliverable?

  The team had strong trace artifacts in the repository (verification scripts, configuration files, and integration checklists), which made it possible to connect implemented functionality to explicit V\&V evidence quickly.

  \item What pain points did you experience during this deliverable, and how
    did you resolve them?

  The largest pain point was uneven availability of quantitative test-result logs across all requirement areas. We addressed this by separating evidence into three categories: executed checks, artifact-based verification, and planned-but-not-yet-measured tests.

  \item Which parts of this document stemmed from speaking to your client(s) or
  a proxy (e.g. your peers)? Which ones were not, and why?

  Requirement priorities around scholarly usability, reconstruction workflows, and transparency of ML outputs reflect advisor and client priorities. Low-level implementation validation (processor registration, schema fields, config correctness) was driven primarily by engineering artifacts rather than direct client interaction.

  \item In what ways was the Verification and Validation (VnV) Plan different
  from the activities that were actually conducted for VnV? If there were
  differences, what changes required the modification in the plan? Why did
  these changes occur? Would you be able to anticipate these changes in future
  projects? If there weren't any differences, how was your team able to clearly
  predict a feasible amount of effort and the right tasks needed to build the
  evidence that demonstrates the required quality? (It is expected that most
  teams will have had to deviate from their original VnV Plan.)

  The plan defined broad FR and NFR test suites, including load, reliability, and usability studies. In practice, a larger portion of completed evidence became integration-centric for active ML pipeline features, especially script-type classification. This deviation was caused by time and environment constraints typical of ML-heavy projects (dependency setup, compute requirements, and rapidly evolving feature scope). In future projects, we would schedule explicit milestones for producing standardized quantitative result artifacts (performance logs, usability summaries, and coverage reports) earlier, so final reporting has more uniform empirical depth across all requirement categories.
\end{enumerate}

\end{document}